---
title: "UTS DMKM"
author: "Moch Izza Z S (221810422)"
date: "27/10/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"party" akan digunakan untuk membuat visualisasi dari decision tree.

"psych" akan digunakan untuk melihat korelasi antar variabel.

"caret" digunakan untuk membuat confusion matriks dan melihat akurasi model.

```{r message=FALSE, warning=FALSE}
library(caret)
library(party)
library(psych)
```

Data diunduh dan kemudian diberikan nama variabel supaya bisa dilihat dengan rapi

Definisi data berupa :

1. name: Name of the country concerned

2. landmass: 1=N.America, 2=S.America, 3=Europe, 4=Africa, 4=Asia, 6=Oceania

3. zone: Geographic quadrant, based on Greenwich and the Equator; 1=NE, 2=SE, 3=SW, 4=NW

4. area: in thousands of square km

5. population: in round millions

6. language: 1=English, 2=Spanish, 3=French, 4=German, 5=Slavic, 6=Other Indo-European, 7=Chinese, 8=Arabic, 9=Japanese/Turkish/Finnish/Magyar, 10=Others

7. religion: 0=Catholic, 1=Other Christian, 2=Muslim, 3=Buddhist, 4=Hindu, 5=Ethnic, 6=Marxist, 7=Others

8. bars: Number of vertical bars in the flag

9. stripes: Number of horizontal stripes in the flag

10. colours: Number of different colours in the flag

11. red: 0 if red absent, 1 if red present in the flag

12. green: same for green

13. blue: same for blue

14. gold: same for gold (also yellow)

15. white: same for white

16. black: same for black

17. orange: same for orange (also brown)

18. mainhue: predominant colour in the flag (tie-breaks decided by taking the topmost hue, if that fails then the most central hue, and if that fails the leftmost hue)

19. circles: Number of circles in the flag

20. crosses: Number of (upright) crosses

21. saltires: Number of diagonal crosses

22. quarters: Number of quartered sections

23. sunstars: Number of sun or star symbols

24. crescent: 1 if a crescent moon symbol present, else 0

25. triangle: 1 if any triangles present, 0 otherwise

26. icon: 1 if an inanimate image present (e.g., a boat), otherwise 0

27. animate: 1 if an animate image (e.g., an eagle, a tree, a human hand) present, 0 otherwise

28. text: 1 if any letters or writing on the flag (e.g., a motto or slogan), 0 otherwise

29. topleft: colour in the top-left corner (moving right to decide tie-breaks)

30. botright: Colour in the bottom-left corner (moving left to decide tie-breaks)

```{r}
dataset <- read.csv("E:/UTS/DMKM/DATA/flag.csv", sep = ",")
head(dataset)
```

Data terlihat bagus,

Kemudian masuk ke dalam pengonversian data menjadi bentuk faktor

```{r}
for(i in names(dataset)){
  dataset[,i]= as.factor(dataset[,i])
}
#untuk memastikan, dilihat struktur datanya
str(dataset)
```

Memecah data training 80% dan data test 20%

```{r}
set.seed(123)
sampel <- sample(2,nrow(dataset),replace = T, prob = c(0.8,0.2))
training <- dataset[sampel==1, ]
testing <- dataset[sampel==2, ]

#melihat distribusi data
print(paste("Jumlah training data :", nrow(training)))
print(paste("Jumlah testing data :", nrow(testing)))
```

Langkah selanjutnya membuat model dengan memprediksi religion nya berdasarkan seluruh data

```{r}
dtree <- ctree(religion~., data=training)
plot(dtree)
```

Karena soal yang diminta adalah Klasifikasi/Prediksi agama dari bendera negara, maka variabel yang tidak dibutuhkan, tidak perlu diikutkan

```{r}
truetree <- ctree(religion~bars+strips+colours+red+green+blue+gold+white+black+orange+mainhue+circles+crosses+saltires+quarters+sunstars+crescent+triangle+icon+animate+text+topleft+botright, data=training)
plot(truetree)
```

Hal terakhir yang diperlukan adalah membuat Confusion Matrix

```{r}
prediksi <- predict(truetree, testing)
confusionMatrix(table(prediksi,testing$religion))
```

Intepretasi :